Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-04 manuscript.tex
5 updates

In this Section we present the analysis conducted on Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the usual approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}. For all the stars that we considered in the present work, we selected only the CCFs that were derived from spectra that had at least a SNR at 550 nm of 10.

@@

\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal density} \label{sec:alphacentb}

We analyzed $1808$ CCFs derived from spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph. Note that more observations have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}. We chosen those observations as they represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.

We begin the analysis by evaluating the correlation between $\gamma$ and BIS SPAN. 
In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$. This strong correlation shows that $\gamma$ and BIS SPAN are measuring in a very similar way the CCF asymmetry. This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.
%\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.

>>>>

In this Section we present the analysis conducted on the star Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec. \ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF. 
%to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. 
Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR at 550 nm of 10 were selected.

@@

\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}

There were $1808$ CCFs analyzed that were derived from the spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph. Note that more observations were carried out this year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}. 
The selected observations should represent the best sampled and most precise RV data set available for Alpha Centauri B \jessi{I added ``Alpha Centauri B'' - if the previous statement was to be more general, please remove} showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.

First, the correlation between $\gamma$ and BIS SPAN is evaluated.
In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$. This strong correlation suggests that the $\gamma$ and BIS SPAN are measuring a similar asymmetry for the CCF. This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.
%\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
